The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-30 Writeup/paper_v3.tex
deal with Tim question re: unclassified vs. neutral, and 0.4-0.55

We thus identify the regions $z=0.30-0.40$, $0.65-0.75$, and
$0.80-0.85$ as overdense; $z=0.55-0.65$ and $0.75-0.80$ as underdense; and $z=0.40-0.55$ as unclassified. 
%Although, the $z=0.40-0.55$ bin appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.

>>>>

We thus identify the regions $z=0.30-0.40$, $0.65-0.75$, and
$0.80-0.85$ as overdense; $z=0.55-0.65$ and $0.75-0.80$ as underdense;
\rachel{and we defer classication of the somewhat ambiguous range from
  $z=0.40-0.55$ until Sec.~\ref{sub:volumelimiting}. }
%Although, the $z=0.40-0.55$ bin appears to be underdense, for reasons mentioned in \S\ref{sub:volumelimiting}, we will not call them underdense.
